Implicit yaddayadda

### 2011-10-27 papers/PLDI2012/implicitization.tex
en bloc analysis

\usepackage{listings}
\lstset{language=C,mathescape=true,numbers=left,numbersep=0.8ex,tabsize=2} % basicstyle={\rm\fontfamily{ppl}\selectfont} trop reconnaissable

@@

This motivates a key implement decision of our tool: only those variables $v_1,\dots,v_n$ that are not defined by arithmetic operations are retained as coordinates in the abstract domain (e.g. as dimensions in polyhedra). A basic block of code therefore amounts to a \emph{parallel assignment} operation
$(v_1,\dots,v_n) \allowbreak\mapsto\allowbreak
(f_1(v_1,\dots,v_n), \allowbreak, \dots, \allowbreak
 f_n(v_1,\dots,v_n))$;
such operations are directly supported by APRON.
A first benefit is to limit the number of dimensions in the abstract values, since polyhedra libraries typically perform worse with higher dimensions.
A second benefit is that the abstract operation for a single path in path-focusing methods also is a (large) parallel assignment.

>>>>

\usepackage{listings}
\lstset{language=C,mathescape=true,numbers=left,numbersep=0.8ex,tabsize=2,breaklines=true} % basicstyle={\rm\fontfamily{ppl}\selectfont} trop reconnaissable

@@

This motivates a key implement decision of our tool: only those variables $v_1,\dots,v_n$ that are not defined by arithmetic operations are retained as coordinates in the abstract domain (e.g. as dimensions in polyhedra). A basic block of code therefore amounts to a \emph{parallel assignment} operation
$(v_1,\dots,v_n) \allowbreak\mapsto\allowbreak
(f_1(v_1,\dots,v_n), \allowbreak, \dots, \allowbreak
 f_n(v_1,\dots,v_n))$;
such operations are directly supported by APRON. This has three benefits:
(i) it limits the number of dimensions in the abstract values, since polyhedra libraries typically perform worse with higher dimensions;
(ii) the abstract operation for a single path in path-focusing methods also is a (large) parallel assignment;
(iii) as suggested by \citet{DBLP:conf/vmcai/Mine06}, this approach is more precise than running abstract operations for each program line separately:
for instance, for \lstinline|y=x; z=x-y;| with precondition $x \in [0,1]$, a line-by-line interval analysis obtains $y \in [0,1]$ and $z \in [-1,1]$ while our ``en bloc'' analysis symbolically simplifies $z = x - x = 0$ and thus $z \in [0,0]$.
